\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Sakthi Harish M} \\
\indent 109/31, Ashok Nagar, \\
\indent Poolavadi Road, Ellis Nagar (Post), \\
\indent Dharapuram (T.N., INDIA) - 638657\\
\indent Email-id : \textbf{sakthiharish0001@gmail.com} \\
\indent Mobile No.: \textbf{8300399225} \\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{Specialization} & \textbf{Institute} & \textbf{Year} & \textbf{CGPA\%} \\
\hline
Under Graduation & \textit{Mechanical Engineering} & GCT, Coimbatore & 2023 & 8.17 (Sem-7)\\
HSC & \textit{State Board (TN)} & Veveaham Hr. Sec. School & 2019 & 89\% \\
SSLC & \textit{State Board (TN)} & Veveaham Hr. Sec. School & 2017 & 96.4\% \\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{ABOUT} }\\[\lsep]
\begin{itemize}
\item \noindent A left-brained engineering student with first-principles thinking.
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Tools} (Solidworks, Catia, Ansys, Vim, \LaTeX, MS Excel, GSuite Apps).
\item \noindent \textbf{Languages} (C), \textbf{Script} (Python)
\item \noindent \textbf{Operating Systems} (Linux, Windows).
\end{itemize}

\resheading{\textbf{PROJECT WORKS} }\\[\lsep]
\begin{itemize}
\item \textbf{PVA/GO/SDS based nanofibrous air filtration membrane with GO/Bamboo Charcoal nylon sheets as secondary air filtration layers
} (Research Project - Main) \\
 \emph{(Guide:Dr. Rajeswari B.
	, Feb'23 - Apr'23)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective : Provide a recyclable air filter solution for HEPA filters used in the HVAC systems in vehicles
	\item The nanofibrous filter could be applied together with nylon sheets treated with TBT+Ethanol solution to provide a better filtering capability

	\item The GO and PVA forms an extremely stable chemical bond, resulting in a solution that could be left untouched for weeks

	\end{itemize}

\item \textbf{Analysis of AirFoil Deformation on long-time Exposure to Sunlight
} (Research Project - Mini) \\
 \emph{(Guide:Dr. Rajeswari B.
, Oct'22 - Dec'22)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective: Define the deformation of 3D-printed PLA-based Airfoils due to sunlight and find the best in-fill pattern with minimal deformation.
	\item The 'Grid' in-fill pattern is found to be the sweetspot between good integrity and light weight.
	\end{itemize}
\end{itemize}

\resheading{\textbf{MEMBERSHIPS AND VOLUNTEERING} }\\[\lsep]
\begin{itemize}
\item \textbf{SAE Screwtinizers GCT
} (Chassis and Ergonomics, Sales and Business) \\
\emph{(Guide: Dr. Periyasamy K.
, Aug'21 - Feb'23)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Design Rollcage framework.
	\end{itemize}
\item \textbf{Centaurus Aerospace Society GCT
} (Manufacturing team) \\
\emph{(Guide: Prof. Parimala M. 
, Mar'22 - Feb'23)} 

\item \textbf{Ys Youth Club GCT
} (Executive Member) \\
\emph{(Aug'21 - Mar'22)} 
\end{itemize}
		
\resheading{\textbf{MISCELLANEOUS} }\\[\lsep]
\begin{itemize}
\item \textbf{Strength} (First-Principles thinking, Able to install and maintain most of the "computer stuff"(PCs, Printers, Wifi, etc.,))
\item \textbf{Interests} (Computers, Self-driving cars and softwares, AI, Films, Politics)
\item \textbf{Hobbies} (Reading books, Movies and generally learning new stuff)
\end{itemize}

\end{document}

